---
title: "Penguins ANOVA"
author: "Becky Clow"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read- in penguins.csv data

```{r, include=FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read.csv("penguins.csv")

```

Our question:

Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, and Adelie)?

1. Do some exploring

New functions: with + table for easy counting over multiple factors 

update species name using case_when

```{r}

counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>% 
  mutate(common_name = 
           case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )) %>% 
  select(-species) %>% #takes out species
  filter(sex == "FEMALE")

```

-Exploratory graphs
-Summary statistics
-Levenne's tests for equal variances
-one-way ANOVA
-pot-hoc test

```{r}

hists <- ggplot(penguins2, aes(x = flipper_length)) +
  geom_histogram(aes(fill = common_name)) +
  facet_wrap(~ common_name)

hists

qqs <- ggplot(penguins2, aes(sample = flipper_length)) +
  geom_qq() +
  facet_wrap(~ common_name)

qqs

# Levene's test for equal variances ( greater than 2 groups.... if you have two groups, use the F test for equal variances)

# We will use the funtion leveneTest form the 'car' package

#H0: Variances equal
#HA: Variances unequal

penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2) #testing variances of flipper lenght between diff species
penguin_levene

# We retain the null hypothesis of equal variances (p = 0.06)

variances <- penguins2 %>% # to create a summary table to represent the variances of the three different groups
  group_by(common_name) %>% 
  summarize(
    variance = var(flipper_length)
  )

variances # see the variances are similar enough

```

