---
title: "Penguins ANOVA"
author: "Becky Clow"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read- in penguins.csv data

```{r, include=FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read.csv("penguins.csv")

```

Our question:

Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, and Adelie)?

1. Do some exploring

New functions: with + table for easy counting over multiple factors 

update species name using case_when

```{r}

counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>% 
  mutate(common_name = 
           case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )) %>% 
  select(-species) %>% #takes out species
  filter(sex == "FEMALE")

```

-Exploratory graphs
-Summary statistics
-Levenne's tests for equal variances
-one-way ANOVA
-pot-hoc test
